FRB 121102: Very Large Array Burst Properties and Implications for Overall FRB Population

### 2016-11-12 repeater-vladata.tex
added ref
added figure and makefile
added some text from first paper. details of multi-telescope coverage

All observations in August and Septmeber were searched in quasi real-time by a prototype version of \rf. \rf is a real-time, fast imaging transient search system. The current, prototype runs on existing hardware of the VLA correlator backend, while the future \rf will run on a dedicated GPU cluster. The transient search pipeline software is called ``rtpipe''\footnote{See \url{https://github.com/caseyjlaw/rtpipe}} and is mostly written in Python.

@@

@@

\subsection{Green Bank Telescope}

@@

Computational notebooks to reproduce the transient detection and localization can be found at \url{https://github.com/caseyjlaw/FRB121102}. VLA data are available at \url{https://doi.org/10.7910/DVN/TLDKXG}.

@@

@@

@@

>>>>

All observations in August and Septmeber were searched in quasi real-time by a prototype version of \rf. \rf\ is a real-time, fast imaging transient search system. The current, prototype runs on existing hardware of the VLA correlator backend, while the future \rf\ will run on a dedicated GPU cluster. The transient search pipeline software is called ``rtpipe''\footnote{See \url{https://github.com/caseyjlaw/rtpipe}} and is mostly written in Python.

@@

% from the first paper
During the joint Arecibo-VLA campaign, Arecibo observed with the L-wide receiver, which has an observational frequency range of 1.15 to 1.73~GHz and a full width at half maximum beam size of 3.3 arcmin. The PUPPI pulsar backend was used to record total intensity spectra with time and frequency resolutions of 10.24~$\mu$s and 1.5625~MHz, respectively, and full Stokes polarization information. Each frequency channel was coherently dedispersed to 557~\dmu, thereby eliminating intra-channel dispersion smearing. PUPPI covers a total of 800~MHz of bandwidth centred at 1380.78125~MHz, but only $\sim$ 620~MHz of this band is usable due to radio frequency interference and receiver sensitivity roll-off at the band edges.

@@

\subsection{AMI}

@@

Computational notebooks to reproduce the transient detection and localization can be found at \url{https://github.com/caseyjlaw/FRB121102}. Time cut-out visibility data are available at \url{https://doi.org/10.7910/DVN/TLDKXG}. Original visibility data are available under VLA program codes 16A-459 and 16A-496 and can be downloaded at \url{http://archive.nrao.edu}.

@@

Arecibo had coverage for 57638, 57643, 57645, 57648, and 57649. For 57643 observing was at C band only. At 57648, a burst is seen at 3757s, coincident with the VLA burst.

Effelsberg had simultaneous coverage for bursts on MJD 57648 and 57649. No simultaneous detections.

AMI had simultaneous coverage for bursts on 57643, 57645, 57648, and 57649.

@@

\cite{2016MNRAS.458L..89C}

\begin{figure}[htb]
\begin{center}
\includegraphics[width=0.9\columnwidth]{lombscargle}
\caption{Lomb-Scargle periodogram.
\label{fig:ls}}
\end{center}
\end{figure}

@@

% from first paper
For a nominal Gpc distance $D$ corresponding to redshifts $z\lesssim 0.3$, the received fluence $A_{\nu}$ from each burst implies  a burst energy
$$E_{\rm burst} = 4\pi D^2 (\delta\Omega/4\pi) A_{\nu} \Delta\nu
\approx 10^{38}\, {\rm erg}\,(\delta\Omega/4\pi) D_{\rm Gpc}^2  (A_{\nu} / 0.1\ {\rm Jy\ ms}) \Delta\nu_{\rm GHz}.$$
The unknown  emission solid angle $\delta\Omega$
could be very small due to relativistic beaming, and together with a distance possibly much smaller than 1~Gpc, could reduce the energy requirement significantly.  However, the {\it total} energy emitted could be larger depending on the duration of the emission in the source frame and other model-dependent details.
Either way, the burst energies from \frb\ are not inconsistent with those that might be expected from the magnetosphere of a compact object\cite{cw16}.
